\MakeUppercase{The Structure of $k$-Planar Graphs}

### 2020-03-26 k-planar.tex
Small changes

Apex-minor-free graphs, addressed by \cref{ApexMinorFree}, are the largest minor-closed class that admit bounded layered partitions~\citep{dujmovic.joret.ea:planar}. However, the family of $k$-planar graphs is not minor-closed.  A graph $G'$ obtained from a $k$-planar graph $G$ by edge deletions and edge contractions may or may not be $k$-planar. \snote{DCG Reviewer \#1 writes: \emph{Isn't this trivial? A grid with all
diagonals will do.}  Is the reviewer correct? If so, what to do?} Indeed, \citet{dujmovic.eppstein.ea:structure} construct 1-planar graphs that contain arbitrarily large complete graph minors. Our results for $k$-planar graphs are the first of this type for a non-minor-closed class.

The following result is the main theorem of the paper. Loosely speaking, it shows that if a graph $G$ admits bounded layered partitions, then so to does $G^\PP$ for every $(k,d)$-shortcut system $\PP$ of $G$.

>>>>

Apex-minor-free graphs, addressed by \cref{ApexMinorFree}, are the largest minor-closed class that admit bounded layered partitions~\citep{dujmovic.joret.ea:planar}. However, the family of $k$-planar graphs is not minor-closed.  A graph $G'$ obtained from a $k$-planar graph $G$ by edge deletions and edge contractions may or may not be $k$-planar. \snote{DCG Reviewer \#1 writes: \emph{Isn't this trivial? A grid with all
diagonals will do.}  The other reviewer write: \emph{Well,
such a construction is trivial: just take grids with both diagonals in
every cell.}  In response, I changed the following sentence from ``construct'' to ``observe''. Ok?} Indeed, \citet{dujmovic.eppstein.ea:structure} observe that even 1-planar graphs may contain arbitrarily large complete graph minors. Our results for $k$-planar graphs are the first of this type for a non-minor-closed class.

The following result is the main theorem of the paper. Loosely speaking, it shows that if a graph $G$ admits bounded layered partitions, then so too does $G^\PP$ for every $(k,d)$-shortcut system $\PP$ of $G$.
